---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)


```

```{css}


```


##Overview of the Data
In this report, we are analyzing a dataset of food delivery orders. The dataset contains information on different platforms used for ordering, the types of restaurants, total order amounts, and customer ratings.

We aim to explore key factors like delivery times, ratings, and the correlation between platform choices and customer satisfaction.

##Delivery Time Analysis
We begin by analyzing the average delivery time across different food delivery platforms.




```{r}
library(dplyr)
library(ggplot2)


# Load the data
logged_data <- read.csv("C:/Users/wany840/OneDrive - The University of Auckland/Documents/Project 2/foodsurvey.csv")

# Rename columns for easier understanding
latest_data <- logged_data %>%
  rename(
    Platform = `Which.food.delivery.platform.was.used.for.this.order.`,
    RestaurantType = `What.type.of.restaurant.was.this.order.from.`,
    TotalAmount = `What.was.the.total.amount.of.the.order...Currency..NZD.`,
    OrderTime = `Order.Time..Multiple.Choice.`,
    DeliveryTime = `How.many.minutes.did.it.take.from.ordering.to.delivery.`,
    DeliveryAttitude = `How.was.the.delivery.person.s.attitude.`,
    Rating = `X...How.would.you.rate.this.food.delivery.experience...1...Very.poor..10...Excellent...`
  )

# ---- Descriptive Statistics ----

# 1. Calculate the mean, median, and standard deviation of TotalAmount and DeliveryTime
mean_total_amount <- mean(latest_data$TotalAmount, na.rm = TRUE)
median_total_amount <- median(latest_data$TotalAmount, na.rm = TRUE)
sd_total_amount <- sd(latest_data$TotalAmount, na.rm = TRUE)

mean_delivery_time <- mean(latest_data$DeliveryTime, na.rm = TRUE)
median_delivery_time <- median(latest_data$DeliveryTime, na.rm = TRUE)
sd_delivery_time <- sd(latest_data$DeliveryTime, na.rm = TRUE)


# Average delivery time by platform
ggplot(latest_data, aes(x = Platform, y = DeliveryTime)) +
  stat_summary(fun = mean, geom = "bar", fill = "#FF5733") +
  labs(title = "Average Delivery Time by Platform", x = "Platform", y = "Average Delivery Time (Minutes)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
