---
title: My dynamic report
output: html_fragment
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```


##Overview of the Data
In this report, we are analyzing a dataset of food delivery orders. The dataset contains information on different platforms used for ordering, the types of restaurants, total order amounts, and customer ratings.

We aim to explore key factors like delivery times, ratings, and the correlation between platform choices and customer satisfaction.

##Delivery Time Analysis
We begin by analyzing the average delivery time across different food delivery platforms.

```{r}




csv_file <- "https://docs.google.com/spreadsheets/d/1RE0pUxFUy1zrV9Y24F2c2uGjPe4vTLKzYF0eNm_4qaA/export?format=csv"

logged_data <- read.csv(csv_file)



# Rename columns for easier understanding
latest_data <- logged_data %>%
  rename(
    Platform = `Which.food.delivery.platform.was.used.for.this.order.`,
    RestaurantType = `What.type.of.restaurant.was.this.order.from.`,
    TotalAmount = `What.was.the.total.amount.of.the.order...Currency..NZD.`,
    OrderTime = `Order.Time..Multiple.Choice.`,
    DeliveryTime = `How.many.minutes.did.it.take.from.ordering.to.delivery.`,
    DeliveryAttitude = `How.was.the.delivery.person.s.attitude.`,
    Rating = `How.would.you.rate.this.food.delivery.experience...1...Very.poor..10...Excellent.`
  )


# ---- Descriptive Statistics ----

# Calculate the mean, median, and standard deviation of TotalAmount and DeliveryTime
mean_total_amount <- mean(latest_data$TotalAmount, na.rm = TRUE)
median_total_amount <- median(latest_data$TotalAmount, na.rm = TRUE)
sd_total_amount <- sd(latest_data$TotalAmount, na.rm = TRUE)

mean_delivery_time <- mean(latest_data$DeliveryTime, na.rm = TRUE)
median_delivery_time <- median(latest_data$DeliveryTime, na.rm = TRUE)
sd_delivery_time <- sd(latest_data$DeliveryTime, na.rm = TRUE)

# Calculate platform statistics directly from latest_data
fastest_platform <- latest_data %>%
  group_by(Platform) %>%
  summarise(avg_delivery = mean(DeliveryTime, na.rm = TRUE)) %>%
  filter(avg_delivery == min(avg_delivery, na.rm = TRUE))

top_rated_platform <- latest_data %>%
  group_by(Platform) %>%
  summarise(avg_rating = mean(Rating, na.rm = TRUE)) %>%
  filter(avg_rating == max(avg_rating, na.rm = TRUE))


# Average delivery time by platform
ggplot(latest_data, aes(x = Platform, y = DeliveryTime)) +
  stat_summary(fun = mean, geom = "bar", fill = "#FF5733") +
  labs(title = "Average Delivery Time by Platform", x = "Platform", y = "Average Delivery Time (Minutes)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


Customer Rating Analysis
Next, we analyze the average ratings across different platforms.

```{r}

# Average rating by platform
ggplot(latest_data, aes(x = Platform, y = Rating)) +
  stat_summary(fun = mean, geom = "bar", fill = "#4CAF50") +
  labs(title = "Average Rating by Platform", x = "Platform", y = "Average Rating") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# Generate dynamic report
report_text <- paste(
  "FOOD DELIVERY PERFORMANCE REPORT",
  "\n\nFastest Delivery Platform:",
  "\nPlatform:", fastest_platform$Platform,
  "\nAverage Delivery Time:", round(fastest_platform$avg_delivery, 1), "minutes",
  
  "\n\nTop-Rated Platform:", 
  "\nPlatform:", top_rated_platform$Platform,
  "\nAverage Rating:", round(top_rated_platform$avg_rating, 1), "stars",
  
  "\n\nReport generated on:", Sys.Date(),
  sep = ""
)

# Print the report
cat(report_text)

```


## extra( Dynamic Commentary Based on Data) just for creativity

```{r}

library(dplyr)
library(ggplot2)

latest_data <- logged_data %>%
  rename(
    Platform = `Which.food.delivery.platform.was.used.for.this.order.`,
    RestaurantType = `What.type.of.restaurant.was.this.order.from.`,
    TotalAmount = `What.was.the.total.amount.of.the.order...Currency..NZD.`,
    OrderTime = `Order.Time..Multiple.Choice.`,
    DeliveryTime = `How.many.minutes.did.it.take.from.ordering.to.delivery.`,
    DeliveryAttitude = `How.was.the.delivery.person.s.attitude.`,
    Rating = `How.would.you.rate.this.food.delivery.experience...1...Very.poor..10...Excellent.`
  ) %>%  # <- 

  mutate(
    # Simplify the name, e.g., L+D = Lunch + Doordash
    Time_Type = paste0(
      substr(OrderTime, 1, 1),  # Take the first letter (L/D)
      "+",
      substr(RestaurantType, 1, 1) # Take the first letter of restaurant type
    )
  )




# count average
summary_data <- latest_data %>%
  group_by(Time_Type, Platform) %>%
  summarise(
    avg_delivery_time = mean(DeliveryTime, na.rm = TRUE),
    avg_rating = mean(Rating, na.rm = TRUE),
    .groups = "drop"
  )


small_font_theme <- theme(
  axis.text = element_text(size = 8),
  axis.title = element_text(size = 9),
  plot.title = element_text(size = 10),
  legend.text = element_text(size = 8),
  legend.title = element_text(size = 9)
)

# delivery time plot
ggplot(summary_data, aes(x = Time_Type, y = avg_delivery_time, fill = Platform)) +
  geom_col(position = position_dodge(0.8), width = 0.7) +
  labs(title = "Avg Delivery Time by Platform", 
       x = "Meal Time + Cuisine Type (L/D+W/A/L)", 
       y = "Delivery Time (min)") +
  small_font_theme

# rating table
ggplot(summary_data, aes(x = Time_Type, y = avg_rating, fill = Platform)) +
  geom_col(position = position_dodge(0.8), width = 0.7) +
  labs(title = "Avg Rating by Platform", 
       x = "Meal Time + Cuisine Type (L/D+W/A/L)", 
       y = "Rating (1-10)") +
  small_font_theme
# Find the platform with the highest average rating for each Time_Type
highest_rating <- latest_data %>%
  group_by(Time_Type) %>%
  mutate(
    highest_rating = max(Rating, na.rm = TRUE)
  ) %>%
  filter(Rating == highest_rating) %>%
  select(Time_Type, Platform, Rating) %>%
  distinct()

# Find the platform with the fastest delivery time for each Time_Type
fastest_delivery <- latest_data %>%
  group_by(Time_Type) %>%
  mutate(
    fastest_delivery_time = min(DeliveryTime, na.rm = TRUE)
  ) %>%
  filter(DeliveryTime == fastest_delivery_time) %>%
  select(Time_Type, Platform, DeliveryTime) %>%
  distinct()

# Generate report
report <- paste(
  "Report on Best Performing Platform for Each Time + Cuisine Type\n",
  "-------------------------------------------------------------\n",
  paste(sapply(1:nrow(highest_rating), function(i) {
    paste0("For ", highest_rating$Time_Type[i], ", the platform with the highest rating is ", 
           highest_rating$Platform[i], " with an average rating of ", highest_rating$Rating[i], ".")
  }), collapse = "\n"),
  "\n",
  paste(sapply(1:nrow(fastest_delivery), function(i) {
    paste0("For ", fastest_delivery$Time_Type[i], ", the platform with the fastest delivery time is ", 
           fastest_delivery$Platform[i], " with an average delivery time of ", fastest_delivery$DeliveryTime[i], " minutes.")
  }), collapse = "\n"),
  sep = "\n"
)

# Print the report
cat(report)

```
